---
name: Filip
surname: Horvat
position: "Bioinformatician"
address: "Institute of Molecular Genetics, Prague, Czech Republic"
# profilepic: "./img/me.jpg"
phone: +385 91 728 4868
email: "fihorvat@gmail.com"
github: fhorvat
linkedin: filip-horvat-6a8538b2
orcid: 0000-0002-1896-7645
# googlescholar: "aA_cIdYAAAAJ"
date: "`r  Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%B %Y')`"
# aboutme: "Bioinformatician and a PhD student at the Laboratory of Epigenetic Regulations"
headcolor: 990000 # 464646 for all black
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
    keep_tex: true
    show_footer: true
    includes:
      in_header: header.txt
    pandoc_args: ["--lua-filter=lua/strong.lua"] 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)
library(dplyr)
library(stringr)
library(kableExtra)
```

# Professional Profile

Highly skilled and experienced computational biologist finishing a PhD in the field. Strong expertise in developing and implementing computational methods for analyzing complex biological data, including genomic and transcriptomic data. Proficient in programming languages such as R and Bash, with experience working in Linux environments. Extensive experience collaborating with multidisciplinary and international teams of scientists on elucidating mechanisms of various biological processes. Seeking a challenging role where my skills and experience can be leveraged to advance scientific discovery and bridge the gap between the computational and experimental research. 


# Professional Experience

```{r employment, eval = T}
tribble(
  ~what, ~when, ~with, ~where, ~why,
  "PhD student - computational research", "2017 - current", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Computational analysis and integration of high-throughput datasets",
    "PhD student - computational research", "2017 - current", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Conducting highly customized analyses and visualizations of complex biological data in R",
  "PhD student - computational research", "2017 - current", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Developing pipelines that automate processing of next generation sequencing datasets generated in the lab",
  "PhD student - computational research", "2017 - current", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Bioinformatic contribution to 10 high-level publications",
  "Specialist of science and research - computational research", "2016 - 2017", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Statistical and differential expression analysis of RNA-seq datasets",
  "Intern - computational research", "2015 - 2016", "University of Zagreb, Faculty of Science, Bioinformatics Group", "Zagreb", "Management, interpretation, visualization, and statistical analysis of high-throughput sequencing data",
  "Intern - laboratory research", "Apr 2015 - Sep 2015", "Max F Perutz Laboratories, DNA Damage Response and Transcription Regulation", "Vienna", "Hands-on experience with various techniques such as PCR, gel electrophoresis, cell culture and DNA extraction"
) %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where, 
                   why = why)
```


# Education

```{r education}
tribble(
  ~what, ~when, ~with, ~where, 
  "PhD in Developmental and Cell Biology", "2017 - current", "Charles University, Faculty of Science","Prague",
  "Master in Molecular Biology", "2013 - 2016", "University of Zagreb, Faculty of Science", "Zagreb",
  "Bachelor in Molecular Biology", "2009 - 2013", "University of Zagreb, Faculty of Science", "Zagreb"
) %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where)
```

\pagebreak

# Skills and Qualifications 

```{r skills, eval = T}
tribble(
  ~with, ~what,
  "Programming languages", "R (advanced), Bash (intermediate), Python (beginner)",
  "R framework", "Shiny, RMarkdown, Bioconductor, tidyverse, ggplot2, plotly",
  "Other computational tools", "Unix/Linux, Command line interface, Nextflow, Git",
  "Languages", "English (fluent), German (basic), Croatian (native)"
) %>% 
  detailed_entries(with = with,
                   what = what)
```

```{r skills_table, eval = F}
tribble(
   ~`Programming languages`, ~`R framework`, ~`Other computational tools`, 
  "R (advanced) -- Bash (intermediate) -- Python (beginner)",
  "Shiny -- RMarkdown -- Bioconductor -- tidyverse -- ggplot2 -- plotly",
  "Unix/Linux -- Command line interface -- Nextflow -- Git", 
) %>% 
  kable(booktabs = T, align = "c", escape = F, format = "latex") %>% 
  kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") %>% 
  row_spec(0, bold = T, color = "#464646") %>%  
  row_spec(1, bold = F, color = "#464646") %>%  
  column_spec(column = 1:3, width = "5.5cm")

tribble(
  ~Languages, 
  "English (fluent) -- German (basic) -- Croatian (native)"
) %>% 
  kable(booktabs = T, align = "c", escape = F, format = "latex") %>% 
  kable_styling(full_width = F, font_size = 10, latex_options = "HOLD_position") %>% 
  row_spec(0, bold = T, color = "#464646") %>%  
  row_spec(1, bold = F, color = "#464646") %>%  
  column_spec(column = 1, width = "5cm")
```


# Teaching Experience

```{r teaching, eval = T}
tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Computational Genomics module", "2017 - 2023", "University of Zagreb, Faculty of Science, Bioinformatics Group", "Zagreb", "Annual participation as a lecturer in 'Algorithms and programming' course for 2nd year master students - teaching R programming, designing and grading practical homework assignments, designing hackathon sessions and providing consultations to approx. 10 students per year",
  "Summer School in Bioinformatics", "2022", "Mediterranean Institute for Life Sciences", "Split", "Presenting a practical, hands-on lecture on basics of RNA-seq data analysis for 30 participants",
  "Summer School in Bioinformatics", "2022", "Mediterranean Institute for Life Sciences", "Split", "Designing and teaching a 3 day interactive workshop - tutoring 6 participants how to find and download RNA-seq data from published papers, do the quality check, trim adapters and map reads to the genome using Galaxy framework, with subsequent exploratory and differential expression analysis done in R",
) %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where, 
                   why = why)
```


# Peer-reviewed Publications
\footnotesize

```{r}
bibliography_entries("citations.bib")
```


# Book Chapters

```{r}
bibliography_entries("book_chapters.bib")
```

