---
name: Filip
surname: Horvat
# position: "Bioinformatician"
address: "Max Perutz Labs, Vienna, Austria"
profilepic: "./img/me.jpg"
# phone: +xxx xx xxx xxxx
email: "fihorvat@gmail.com"
github: "github.com/fhorvat"
linkedin: "linkedin.com/in/filip-horvat-6a8538b2"
# orcid: "orcid.org/0000-0002-1896-7645"
googlescholar: "scholar.google.com/citations?user=aA_cIdYAAAAJ"
date: "`r  Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%B %Y')`"
aboutme: "Bioinformatics postdoc at the DNA Damage Response and Transcription Regulation Lab"
headcolor: 990000 # 464646 for all black
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
    keep_tex: true
    show_footer: true
    includes:
      in_header: header.txt
    pandoc_args: ["--lua-filter=lua/strong.lua"] 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)
library(dplyr)
library(stringr)
library(kableExtra)
```

# Profile

Highly skilled computational biologist with strong expertise in developing and implementing computational methods for analyzing complex biological data. Proficient in R programming framework and comfortable with working in Linux environments utilizing high-performance clusters. Possesses extensive experience working in multidisciplinary scientific teams on elucidating mechanisms of biological processes.

# Professional Competence
```{r competence_computational, eval = T}
tribble(
  ~with, ~why,
  "Computational biology and bioinformatics", "Extensive experience in analyzing single-cell RNA-seq data, including preprocessing, quality control, normalization, batch effect correction, integration, clustering, differential expression analysis, and trajectory inference",
  "Computational biology and bioinformatics", "Strong background in transcriptomics data analysis: RNA-seq, small RNA-seq and TT-seq",
  "Computational biology and bioinformatics", "Significant expertise with genomics and epigenomics data analysis: ChIP-seq, CUT&RUN, ATAC-seq, WGBS-seq",
  "Computational biology and bioinformatics", "Familiarity with processing datasets produced with 3rd and 4th generation sequencing methods: PacBio, Nanopore",
  "Computational biology and bioinformatics", "Solid understanding of essential machine-learing algorithms"
) %>% 
  detailed_entries(with = with,
                   why = why)
```

```{r competence_table, eval = T}
tribble(
  ~`Programming languages`, ~`R framework`, 
  "R (advanced) | Bash (advanced) | Python (beginner)",
  "Bioconductor | Seurat | Shiny   RMarkdown | tidyverse | ggplot2",
) %>% 
  kable(booktabs = T, align = "c", escape = F, format = "latex") %>% 
  kable_styling(full_width = F, font_size = 11, latex_options = "HOLD_position") %>% 
  row_spec(0, bold = T, color = "#464646") %>%  
  row_spec(1, bold = F, color = "#464646") %>%  
  column_spec(column = 1:2, width = "6.5cm")

tribble(
  ~`Reproducibility and Automation`, ~`General computational tools`, 
  "Nextflow | Git | Docker | Singularity   Conda",
  "Unix/Linux system administration   High-performance clusters (HPC)",
) %>% 
  kable(booktabs = T, align = "c", escape = F, format = "latex") %>% 
  kable_styling(full_width = F, font_size = 11, latex_options = "HOLD_position") %>% 
  row_spec(0, bold = T, color = "#464646") %>%  
  row_spec(1, bold = F, color = "#464646") %>%  
  column_spec(column = 1:2, width = "6.5cm")
```

```{r competence_personal, eval = T}
tribble(
  ~with, ~why,
  "Personal skills", "Highly motivated and dedicated scientist with a passion for learning and implementing new technologies", 
  "Personal skills", "Team player with excellent interpersonal and communication skills",
  "Personal skills", "Proficient in presenting intricate data, as evidenced by peer-reviewed publications",
  "Personal skills", "Strong ability to discuss data, modeling, and analytics with non-computational team members"
  
) %>% 
  detailed_entries(with = with,
                   why = why)

tribble(
  ~`Languages`, 
  "English (fluent) | German (basic)   Croatian (native)",
) %>% 
  kable(booktabs = T, align = "c", escape = F, format = "latex") %>% 
  kable_styling(full_width = F, font_size = 11, latex_options = "HOLD_position") %>% 
  row_spec(0, bold = T, color = "#464646") %>%  
  row_spec(1, bold = F, color = "#464646") %>%  
  column_spec(column = 1, width = "6.5cm")
```

\pagebreak

# Education

```{r education}
tribble(
  ~what, ~when, ~with, ~where, 
  "PhD in Developmental and Cell Biology", "2017 - 2023", "Charles University, Faculty of Science","Prague",
  "Master in Molecular Biology", "2013 - 2016", "University of Zagreb, Faculty of Science", "Zagreb",
  "Bachelor in Molecular Biology", "2009 - 2013", "University of Zagreb, Faculty of Science", "Zagreb"
) %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where)
```

# Professional Experience

```{r employment, eval = T}
tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Postdoc - computational research", "2024 - current", "Max Perutz Labs, DNA Damage Response and Transcription Regulation", "Vienna", "Roles of proteins with SPOC domain in transcription regulation",
  "Postdoc - computational research", "2024 - current", "Max Perutz Labs, DNA Damage Response and Transcription Regulation", "Vienna", "Regulation of neuronal gene expression and differentiation",
  "Postdoc - computational research", "2024 - current", "Max Perutz Labs, DNA Damage Response and Transcription Regulation", "Vienna", "Molecular mechanisms of radiation-induced anti-tumor immunogenicity",
  "PhD student - computational research", "2017 - 2023", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Bioinformatic analysis of RNA dynamics in mammalian oocytes and early embryos",
  "PhD student - computational research", "2017 - 2023", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Developing pipelines for automatic processing of next generation sequencing datasets generated in the lab",
  "PhD student - computational research", "2017 - 2023", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Bioinformatic contribution to 12 high-level publications",
  "Specialist of science and research - computational research", "2016 - 2017", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Statistical and differential expression analysis of RNA-seq datasets"
) %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where, 
                   why = why)
```


# Teaching Experience

```{r teaching, eval = T}
tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Computational Genomics module", "2017 - 2023", "University of Zagreb, Faculty of Science, Bioinformatics Group", "Zagreb", "Annual participation as a lecturer in 'Algorithms and programming' course for 2nd year master students - teaching R programming, designing and grading practical homework assignments, designing hackathon sessions and providing consultations to approx. 10 students per year",
  "Summer School in Bioinformatics", "2022", "Mediterranean Institute for Life Sciences", "Split", "Presenting a practical, hands-on lecture on basics of RNA-seq data analysis for 30 participants",
  "Summer School in Bioinformatics", "2022", "Mediterranean Institute for Life Sciences", "Split", "Designing and teaching a 3 day interactive workshop - tutoring 6 participants how to find and download RNA-seq data from published papers, do the quality check, trim adapters and map reads to the genome using Galaxy framework, with subsequent exploratory and differential expression analysis done in R",
) %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where, 
                   why = why)
```


# Selected Peer-reviewed Publications

\footnotesize

```{r}
bibliography_entries("citations.bib")
```

<!-- For the full list of publications please see: https://scholar.google.com/citations?user=aA_cIdYAAAAJ&hl=en -->