---
name: Filip
surname: Horvat
position: "Bioinformatician"
address: "Institute of Molecular Genetics, Prague, Czech Republic"
profilepic: "./img/me.jpg"
# phone: +xxx xx xxx xxxx
email: "fihorvat@gmail.com"
github: fhorvat
linkedin: filip-horvat-6a8538b2
orcid: 0000-0002-1896-7645
googlescholar: "aA_cIdYAAAAJ"
date: "`r  Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%B %Y')`"
# aboutme: "Bioinformatician and a PhD student at the Laboratory of Epigenetic Regulations"
headcolor: 990000 # 464646 for all black
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
    keep_tex: true
    show_footer: true
    includes:
      in_header: header.txt
    pandoc_args: ["--lua-filter=lua/strong.lua"] 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)
library(dplyr)
library(stringr)
library(kableExtra)
```

# Profile

Highly skilled and experienced computational biologist finishing a PhD in the field with strong expertise in developing and implementing computational methods for analyzing complex biological data. Proficient in programming languages such as R and Bash and comfortable with working in Linux environments utilizing high-performance clusters. Possessing extensive experience collaborating with multidisciplinary and international teams of scientists on elucidating mechanisms of various biological processes. Seeking a challenging role in industry where my skills and experience can be leveraged to advance scientific discovery and bridge the gap between the computational and experimental research. 

# Professional Competence
```{r competence_computational, eval = T}
tribble(
  ~with, ~why,
  "Computational biology and bioinformatics", "Computational integration of high-throughput datasets, from experimental design to data analysis",
  "Computational biology and bioinformatics", "Extensive experience in analysing RNA-seq, small RNA-seq, ChIP-seq, ATAC-seq and WGBS-seq data",
  "Computational biology and bioinformatics", "Familiarity with single-cell genomics and transcriptomics datasets",
  "Computational biology and bioinformatics", "Skilled in curation and managment of both in-house produced as well as publicly availible datasets",
  "Computational biology and bioinformatics", "Experienced in processing datasets produced with 3rd and 4th generation sequencing methods (PacBio, Nanopore)",
  "Computational biology and bioinformatics", "Solid understanding of essential machine-learing algorithms",
  "Computational biology and bioinformatics", "Demonstrated knowledge of various bioinformatic algorithms and procedures, such as sequence alignment, differential expression and gene ontology analysis, genome and transcriptome assembly methods, phylogenetic analysis and variant calling"
  
) %>% 
  detailed_entries(with = with,
                   why = why)
```


```{r competence_personal, eval = T}
tribble(
  ~with, ~why,
  "Personal skills", "Highly motivated and dedicated scientist with a passion for learning and implementing new technologies", 
  "Personal skills", "Team player that thrives in diverse teams, with excellent interpersonal and communication skills",
  "Personal skills", "Proficient in presenting intricate data, as evidenced by peer-reviewed publications",
  "Personal skills", "Strong ability to discuss data, modeling, and analytics with non-computational team members"
  
) %>% 
  detailed_entries(with = with,
                   why = why)
```


```{r competence_table, eval = T}
tribble(
  ~with,
  "Software and languages"
) %>% 
  detailed_entries(with = with)

tribble(
  ~`Programming languages`, ~`R framework`, ~`Other computational tools`, 
  "R (advanced) -- Bash (intermediate) -- Python (beginner)",
  "Shiny -- RMarkdown -- Bioconductor -- tidyverse -- ggplot2 -- plotly",
  "Unix/Linux -- Command line interface -- High-performance clusters -- Nextflow -- Git -- Docker -- Conda", 
) %>% 
  kable(booktabs = T, align = "c", escape = F, format = "latex") %>% 
  kable_styling(full_width = F, font_size = 11, latex_options = "HOLD_position") %>% 
  row_spec(0, bold = T, color = "#464646") %>%  
  row_spec(1, bold = F, color = "#464646") %>%  
  column_spec(column = 1:3, width = "5.5cm")

tribble(
  ~Languages, 
  "English (fluent) -- German (basic) -- Croatian (native)"
) %>% 
  kable(booktabs = T, align = "c", escape = F, format = "latex") %>% 
  kable_styling(full_width = F, font_size = 11, latex_options = "HOLD_position") %>% 
  row_spec(0, bold = T, color = "#464646") %>%  
  row_spec(1, bold = F, color = "#464646") %>%  
  column_spec(column = 1, width = "5cm")
```

\pagebreak

# Education

```{r education}
tribble(
  ~what, ~when, ~with, ~where, 
  "PhD in Developmental and Cell Biology", "2017 - current", "Charles University, Faculty of Science","Prague",
  "Master in Molecular Biology", "2013 - 2016", "University of Zagreb, Faculty of Science", "Zagreb",
  "Bachelor in Molecular Biology", "2009 - 2013", "University of Zagreb, Faculty of Science", "Zagreb"
) %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where)
```

# Professional Experience

```{r employment, eval = T}
tribble(
  ~what, ~when, ~with, ~where, ~why,
  "PhD student - computational research", "2017 - current", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Computational analysis and integration of high-throughput datasets",
  "PhD student - computational research", "2017 - current", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Developing pipelines for automatic processing of next generation sequencing datasets generated in the lab",
  "PhD student - computational research", "2017 - current", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Bioinformatic contribution to 10 high-level publications",
  "Specialist of science and research - computational research", "2016 - 2017", "Institute of Molecular Genetics, Laboratory of Epigenetic Regulations", "Prague", "Statistical and differential expression analysis of RNA-seq datasets",
  "Intern - computational research", "2015 - 2016", "University of Zagreb, Faculty of Science, Bioinformatics Group", "Zagreb", "Management, interpretation, visualization, and statistical analysis of high-throughput sequencing data",
  "Intern - laboratory research", "Apr 2015 - Sep 2015", "Max F Perutz Laboratories, DNA Damage Response and Transcription Regulation", "Vienna", "Hands-on experience with various techniques such as PCR, gel electrophoresis, cell culture and DNA extraction"
) %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where, 
                   why = why)
```


# Teaching Experience

```{r teaching, eval = T}
tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Computational Genomics module", "2017 - 2023", "University of Zagreb, Faculty of Science, Bioinformatics Group", "Zagreb", "Annual participation as a lecturer in 'Algorithms and programming' course for 2nd year master students - teaching R programming, designing and grading practical homework assignments, designing hackathon sessions and providing consultations to approx. 10 students per year",
  "Summer School in Bioinformatics", "2022", "Mediterranean Institute for Life Sciences", "Split", "Presenting a practical, hands-on lecture on basics of RNA-seq data analysis for 30 participants",
  "Summer School in Bioinformatics", "2022", "Mediterranean Institute for Life Sciences", "Split", "Designing and teaching a 3 day interactive workshop - tutoring 6 participants how to find and download RNA-seq data from published papers, do the quality check, trim adapters and map reads to the genome using Galaxy framework, with subsequent exploratory and differential expression analysis done in R",
) %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where, 
                   why = why)
```


# Peer-reviewed Publications

\footnotesize

```{r}
bibliography_entries("citations.bib")
```

<!-- For the full list of publications please see: https://scholar.google.com/citations?user=aA_cIdYAAAAJ&hl=en -->

# Book Chapters

```{r}
bibliography_entries("book_chapters.bib")
```

